---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ECoFarchive
```{r message=FALSE, warning=FALSE, include=FALSE}
library(stringr)
library(badger)
available_releases <- dir("archive") %>%
  str_extract_all('(?<=ECoF_).+?(?=.rds)') %>%
  unlist()
oldest_release <- sort(available_releases)[length(available_releases)]
latest_release <- sort(available_releases)[1]
url <- str_c("https://github.com/mattiaghilardi/ECoFarchive/blob/main/archive/ECoF_", 
             latest_release, 
             ".rds")
download_date <- format(as.Date(Sys.Date(), format = "%Y-%m-%d"), "%d %B %Y")
```

<!-- badges: start -->
`r badge_github_actions("mattiaghilardi/ECoFarchive", "download-ECoF")`
`r badge_license(color = "lightgrey")`
`r badge_custom("latest release", latest_release, "blue", url = url)`
<!-- badges: end -->

This repository serves as the archive of the [Eschmeyer's Catalog of Fishes](https://research.calacademy.org/research/ichthyology/catalog/fishcatmain.asp) (ECoF) (Fricke et al. 2024, Van der Laan et al. 2024), accessed through the [`fishrfun`](https://github.com/mattiaghilardi/fishrfun) R package (currently in development). The oldest available ECoF release is *`r oldest_release`*. The archive is automatically updated every month between the 1^st^ and the 10^th^ with the new release.

### References

Fricke, R., Eschmeyer, W. N. & Van der Laan, R. (eds) 2024.  ESCHMEYER'S CATALOG OF FISHES: GENERA, SPECIES, REFERENCES. (<http://researcharchive.calacademy.org/research/ichthyology/catalog/fishcatmain.asp>). Electronic version accessed `r download_date`.

Van der Laan, R., Fricke, R. & Eschmeyer, W. N. (eds) 2024.  ESCHMEYER'S CATALOG OF FISHES: CLASSIFICATION. (<http://www.calacademy.org/scientists/catalog-of-fishes-classification/>). Electronic version accessed `r download_date`. 
